---
title: "Getting started with binomial"
author: "Everett Fisher"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{binomial-intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## Binomial

The package `"binomial"` contains several funcions for descriptive statistics about binomial distributions.

## Creating a binomial variable

We can create a `"binvar"` object with the function `bin_variable()`

```{r}
bin1 <- bin_variable(trials=5, prob=0.3)
bin1
```

The `"binvar"` object is a list with elements `"trials"` and `"success"`.
You can view more detailed descriptive statistics with `summary()`

```{r}
summary(bin1)
```

Each measure listed in the summary has a standalone function of the form `bin_mean`, `bin_variance`, etc.

## Binomial distributions

You can easily view the distribution of successes over a given amount of trials with  `bin_distribution()`

```{r}
dis1 <- bin_distribution(trials=bin1$trials, prob=bin1$prob)
dis1
```

Or, for cumulative distributions, use `bin_cumulative()`

```{r}
dis2 <- bin_cumulative(trials=bin1$trials, prob=bin1$prob)
dis2
```

## Plotting distributions

The default plotting method for binomial distributions is a histogram.

```{r}
plot(dis1)
```

Cumulative distributions are plotted as line graphs.

```{r}
plot(dis2)
```
