---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is an [R](http://www.r-project.org/) package 
that provides functions for binomial distribution summaries

* `bin_choose()` chooses k from n
* `bin_probability()` computes probability of k success in n trials
* `bin_distribution()` creates object of class "bindis"
* `bin_cumulative()` creates object of class "bincum"
* `bin_variable()` creates object of class "binvar"
* `bin_mean()` computes mean of a binomial distribution
* `bin_variance()` computes variance of a binomial distribution
* `bin_mode()` computes mode of a binomial distribution
* `bin_skewness()` computes skewness of a binomial distribution
* `bin_kurtosis()` computes kurtosis of a binomial distribution


## Motivation

This package has been developed for workout03 of the spring 2019 semester of Stat 133


## Usage

```{r}
library(binomial)
# creating a binvomial variable
bin1 <- bin_variable(trials=5, prob=0.3)
bin1

# cumulative distribution
bin2 <- bin_cumulative(trials=5, prob=0.3)
bin2

# summary
summary(bin1)
```
